Experience Report: Haskell in Computational Biology

### 2012-07-01 mrfy_experience_report.tex
Revised commentary on the code

Despite these non-modular aspects, the search
interface provides ample scope for
experiments.
Random hill climbing took fifty lines of code and one~day to
implement.
Simulated annealing reuses hill climbing's
 \texttt{nextPt} function.
Simulated annealing's  new \texttt{utility} function took ten
lines of code and half an hour to implement.
(Hill climbing accepts a point if and only if it scores better than its
predecessor;
simulated annealing may accept a point that scores worse.)
Our genetic algorithm reuses the same
\texttt{pt0} and \texttt{SearchStop} functions, and its \texttt{utility}
function took only a few lines of code.
But~the recombination of parent
placements in its \texttt{nextPt} function took forty lines of code
and a full day to implement.

We note that the \texttt{SearchStop} functions are not as composable as we
would like, and we would like to have a combinator library for searches.

>>>>

Despite these non-modular aspects, the search
interface provides ample scope for
experiments.
Random hill climbing took 50~lines of code and one~day to
implement.  
Simulated annealing requires only a new
\texttt{utility} function, which took 15~lines of code and half an hour to implement.
(Hill climbing accepts a point if and only if it scores better than its
predecessor;
simulated annealing may accept a point that scores worse.)
Our genetic algorithm reuses the same
\texttt{pt0} and \texttt{SearchStop} functions, and its \texttt{utility}
function took only a few lines of code.
\remark{This claim isn't supported by inspection of the code.}
But~the recombination of parent
placements in its \texttt{nextPt} function took forty lines of code
and a full day to implement.

We're not entirely happy with the way we're writing individual
functions.
In~particular, \texttt{SearchStop} functions aren't composable;
we~can't, for example, combine two functions to say that we'd like to
stop if scores aren't improving or if we've tried a thousand points,
whichever comes first.
Eventually, we'd like to have
combinator libraries for \texttt{SearchStop} and \texttt{nextGen}, at~least.
